%-------------------------
% Resume in Latex
% Author : Avhi Mazumder
% Based off of: https://github.com/AvhiMaz/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Avhi Mazumder} \\ \vspace{1pt}
    \small\href{mailto:avhimazumder5@gmail.com}{\underline{avhimazumder5@gmail}} $|$ \
    \href{https://avhidotsol.xyz/}{\underline{avhidotsol.xyz}} $|$
    \href{https://github.com/AvhiMaz}{\underline{github.com/AvhiMaz}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Assam Downtown University}{Guwahati, Assam}
      {Bachelor of Technology in Computer Science (GPA - 3.36 / 4.0)}{Aug. 2022 -- Present}
    \resumeSubheading
      {Vivekananda Kendra Vidyalaya}{Assam}
      {12th in Science}{Mar. 2019 -- May 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Solanaturbine Advanced SVM Cohort}{Apr. 2025 -- Present}
      {Participant}{Remote}
      \resumeItemListStart
        \resumeItem{Completed an advanced cohort focused on Solana's Sealevel Virtual Machine (SVM), zero-dependency development, and on-chain systems design}
        \resumeItem{Built, tested, and deployed native Solana programs using tools like Pinocchio, native rust and testing framework like mollusk}
      \resumeItemListEnd
    \resumeSubheading
      {Solanaturbine Builders' Cohort}{Jan. 2025 -- Mar 2025}
      {Builder}{Remote}
    \resumeItemListStart
      \resumeItem{Completed builder program focused on Solana smart contract development, SVM internals, and dApp architecture}
      \resumeItem{Built 7–8 smart contracts throughout the cohort covering program design, testing, and deployment using Rust and Anchor}
      \resumeItem{Developed Nestfolio as a capstone project — an AI-powered DAO governance platform}
      \resumeItem{Used Bankrun for high-speed local simulation and testing of Solana programs}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Nestfolio} $|$ \emph{Anchor, Rust, Bankrun, Telegram Bot, React}}{Jan. 2025 -- Mar. 2025}
          \resumeItemListStart
            \resumeItem{Built an AI-powered DAO governance platform enabling users to query, summarize, and vote on proposals via a Telegram bot}
    \resumeItem{Wrote Solana smart contracts using Anchor to manage DAO proposal state, voting logic, and on-chain execution}
    \resumeItem{Used Bankrun for high-speed, local testing of smart contracts with full test coverage}
    \resumeItem{Developed a React frontend for product landing page}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Blink Arena} $|$ \emph{Next.js, Prisma, MongoDB, Solana Blinks, TypeScript, Docker}}{Oct. 2024 -- Nov. 2024}
          \resumeItemListStart
                \resumeItem{Built a platform where users can host or join gaming tournaments directly through Solana Blinks}
    \resumeItem{Integrated wallet-based authentication and instant tournament interactions via Solana Blinks for seamless UX}
    \resumeItem{Won a \$1000 grant from Superteam for innovation in on-chain gaming infrastructure}
    \resumeItem{Developed a scalable backend using Prisma and MongoDB, and styled the frontend with TailwindCSS}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Frontend}{: JavaScript, Typescript, Tailwind, React, Next} \\
     \textbf{Backend}{: Node.js, Express.js, MongoDB} \\
     \textbf{Web3}{: Anchor, Solana, Rust, Pinocchio, Bankrun, Mollusk} \\
     \textbf{Tools}{: Git, Github, Docker, Vim, VS Code, Linux}
    }}
 \end{itemize}

%-----------ACHIEVEMENTS-----------
\section{Achievements}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Grant Reciepent (2x)} $|$ \emph{Solana Foundation and Superteam}}{}
          \resumeItemListStart
            \resumeItem{Awarded a total of \$3000 in grants for building Nestfolio and Blink Arena}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Member} $|$ \emph{Superteam India}}{}
          \resumeItemListStart
                \resumeItem{Selected to join Superteam as a member, a global network of top builders and contributors accelerating the adoption of Solana. Participate in bounties and grants, and build real-world on-chain products alongside the Solana community.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
